%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah
%
% Important note:
% This template requires the resume.cls
% file to be in the same directory as the
% .tex file. The resume.cls file provides
% the resume style used for structuring the
% document.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{changepage}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Joseph Gurr} % Your name
% \address{123 Pleasant Lane \\ City, State 12345} % Your address
% \address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)
\address{joseph.gurr@outlook.com} % Your phone number and email

\begin{document}

This document is created with the \TeX \ typesetting language and kept under version control.
You can find the most recent version \href{https://github.com/joegurr/resume/blob/main/resume.pdf}{here}.

%------------------
% EDUCATION SECTION
%------------------

\begin{rSection}{Education}
    \begin{rSubsection}{University of New South Wales, Australia}{\em 2023 - present}{}{}
        \item Master of Mathematics
    \end{rSubsection}
    \begin{rSubsection}{University of Newcastle, Australia}{\em 2015 - 2019}{}{}
        \item Bachelor of Mathematics (Pure Mathematics) \hfill {\em GAP 6.96/7, WAM 91.39}
    \end{rSubsection}
\end{rSection}

%------------------------
% CERTIFICATES SECTION
%------------------------

\begin{rSection}{Certifications}
    \item AWS Certified Developer - Associate \hfill {\em valid December 2022 - December 2025}
    \item Apache Druid Basics \hfill {\em valid December 2021 - December 2023}
    \item Mental Health First Aid \hfill {\em valid September 2023 - September 2026}
\end{rSection}

%------------------------
% WORK EXPERIENCE SECTION
%------------------------

\begin{rSection}{Work Experience}

    \begin{rSubsection}{Software Engineer at Cartesian Software}{\em August 2023 - present}{}{}
        \item I productionise large energy market optimisation models.
    \end{rSubsection}

    \begin{rSubsection}{Casual Academic at The University of Sydney}{\em February 2023 - June 2023}{}{}
        \item I run linear algebra tutorials for first year science and engineering students. (MATH1002)
    \end{rSubsection}

    \begin{rSubsection}{Consulting Software Engineer}{\em February 2023 - present}{}{}
        \item I offer software engineering consulting and support services as a sole trader.
    \end{rSubsection}

    \begin{rSubsection}{Senior Developer at InterAction}{\em May 2022 - February 2023}{}{}
        \item I began working at InterAction on a 3 month contract to complete some short term application development for a client of theirs.
        There were some issues with the client's budget, so my contract was extended and I began working on improving BAU processes.
        When the application development began I worked on full stack applications using both Laravel (PHP) and Flask (Python).
        These applications included authentication, payment systems, and handling data uploads.
        I met with the clients and scoped out the work. I worked heavily within AWS as a part of this.
        While completing this development work I also worked with the operations team to assist with BAU tasks.
        This involved using the Quadient/GMC software Inspire. At the end of this development work I stayed on a contract to help the client support their application.
    \end{rSubsection}

    \begin{rSubsection}{Sessional Academic at The University of Newcastle}{\em February 2022 - June 2022}{}{}
        \item I ran mathematics tutorials for first year science and engineering students.
        The content included advanced calculus, linear algebra, and differential equations. I received 5 star feedback for my teaching. (MATH1110, MATH1120)
    \end{rSubsection}

    \newpage

    {\bf SwitchDin}

    SwitchDin is a energy startup that is trying to transform the world's energy grids to be highly
    distributed and renewable.

    \begin{adjustwidth}{2em}{}
        \begin{rSubsection}{Data Science Engineer}{\em July 2021 - January 2022}{}{}
            \item My team developed distributed optimisation procedures that run on edge devices (Raspberry Pi) to control
            distributed energy resources. This involved having to run forecasts in real time, solve a convex optimisation problem, process the output, and
            then have the control implemented on an external device. This was done in Python.
        \end{rSubsection}

        \begin{rSubsection}{Data Services Team Lead (acting)}{\em January 2021 - July 2021}{}{}
            \item In the absence of a leader for the newly formed Data Services team I stepped up to the
            challenge and stood in as the temporary team leader. I lead a team of four data science
            professionals. This role included software development, internal and external stakeholder
            management, and management of my team members. Some of my responsibilities included providing
            and managing a performant and cost effective time series database, providing and operating an
            OLAP site used by our external clients, developing forecasting algorithms and collaborating
            with other teams on convex optimisation problems, developing market based decision making
            technologies, and more typical reporting functionality.
        \end{rSubsection}

        \begin{rSubsection}{Web Services Engineer}{\em May 2020 - January 2021}{}{}
            \item I built web and mobile applications using Angular and Ionic.
            I worked closely with our back-end teams, designers, and external customers
            to deliver the best product.
        \end{rSubsection}
    \end{adjustwidth}

    {\bf Heffron}

    Heffron provides administration, education, and other services to assist clients with their
    SMSFs (Self Managed Superannuation Funds). They are specialists in this field.

    \begin{adjustwidth}{2em}{}
        \begin{rSubsection}{}{\em November 2016 - November 2019}{}{}
            \item
            I began at Heffron in a data entry role. I quickly saw ways to automate many parts of my job.
            I taught myself how to write simple programs before taking some software engineering courses at uni.
            In my first year I was responsible for refactoring a critical algorithm that determines payable
            tax for certain SMSFs. This was done in Symfony (a php framework).
            I also worked on front end wizards that were written in KnockoutJS.

            From here I worked on how to make certain parts of the organisation more efficient. I helped increase
            to use of DocuSign by writing extensive internal documentation.
            I worked on assessing the regular expression engine used in one of the major pieces of software that
            the accountants used (Class).

            From here I worked on the massive project of transitioning our technology stack from a Symfony and KnockoutJS stack to a
            serverless architecture using AWS Lambdas (using Typescript). I used DynamoDB and IAM as a part of this. During this
            time I also worked on a customer facing CMS that our marketing team would ultimately manage.
        \end{rSubsection}
    \end{adjustwidth}

    {\bf Mathematics Undergraduate Summer Vacation Scholarship}
    \hfill {\em November 2015 - January 2016} \\
    I worked to develop a greater understanding of linear representations of k-regular
    sequences and Stern's diatomic sequence under the guidance of Associate Professor Michael Coons Jr.

        {\bf Private tutoring} \hfill {\em January 2012 - November 2021} \\
    I have extensive experience tutoring secondary and tertiary students in mathematics,
    physics, chemistry, and statistics.
\end{rSection}

%---------------------
% TECHNOLOGIES SECTION
%---------------------

\begin{rSection}{Technologies/Programming Languages}
    \item {\em * I have worked with this in a professional capacity in a non-trivial way}
    \item {\bf Front-End} HTML* (plus a variety of HTML templating languages like razor*,
    blade*, and jinja2*), CSS* (SASS*, SCSS*), Javascript*/Typescript* (Angular*, Ionic*)
    \item {\bf Back-End} Python* (Django*, Flask*), NodeJS*, Java, PHP* (Laravel*, Symfony*)
    \item {\bf Data} RDBMS (Postgres*, MySQL*, MariaDB, SQLite), NoSQL (DynamoDB*, MongoDB),
    \\ Apache Druid*, Apache Superset*, RabbitMQ*, Kafka*, Redis*, Pandas*/Numpy*/other Python data packages*, R
    \item {\bf Operating Systems} Ubuntu* (16.04, 18.04*, 20.04*), MacOS X, Windows 10
    \item {\bf Other} git* (GitHub*, GitLab*, Bitbucket*), Docker*, AWS* (mainly S3*, Lambda*, APIGateway*, CloudFormation*), Microsoft Azure*,
    \TeX\ (\LaTeX), Atlassian Suite* (JIRA*, Confluence*), Quadient/GMC Inspire*
    \item Other technologies/programming languages I have used in a limited capacity include:
    Ansible, Vue, React, LISP, C, C\texttt{++}, SPSS, MATLAB, Haskell, Docker Swarm, and Kubernetes
    \item I am experienced in CI/CD, TDD, and Agile
\end{rSection}

%------------------------
% ACHIEVEMENTS SECTION
%------------------------

\begin{rSection}{Achievements}
    \item Awarded the New Columbo Plan Mobility Scholarship to participate in \hfill {\em 2018}
    \\ the Reimagining India program
    \item Placed on the Faculty of Science Commendation List \hfill {\em 2015, 2016, 2018}
    \item Awarded the School of Mathematics and Physical Sciences Vacation Scholarship
    \hfill {\em 2015}
    \item Awarded the Shaping Futures Scholarship \hfill {\em 2015} \
    \item Awarded the Vice Chancellor's Scholarship for Academic Excellence in Year 12 \hfill {\em 2015}
\end{rSection}

\begin{rSection}{Hobbies}
    \item Glebe Community Garden Volunteer \hfill {\em February 2023 - present}
    \item Arcadia Park Land Care Volunteer \hfill {\em 2020 - 2022}
    \item Outdoor Activities (rock climbing, hiking, camping)
\end{rSection}

\end{document}
